### 2019-01-02 index.Rmd
Update to v0.0-6
Local commit

@@

@@

>>>>

```{r, echo = FALSE, fig = TRUE, results = 'hide', fig.width = 12, fig.height = 4}
windrose(mod, type = "histogram", mfcol = 3)
```

@@

<p id="hastie2009">
Hastie T, Tibshirani R, Friedman J (2009).
Fitting Logistic Regression Models. In _The Elements of Statistical Learning_
(Chapter 4.4.1), 2_nd_ edition, ISBN 978-0387848570.
<a href="https://web.stanford.edu/~hastie/ElemStatLearn/" target="_blank">PDF download</a>
</p>

@@

<p id="mccullagh1999">
McCullagh P, Nelder JA (1999).
Likelihood functions for binary data. In _Generalized Linear Models_ (Chapter 4.4),
2_nd_ edition, ISBN 0-412-31760-5.
</p>
